### 2023-04-24 manuscript.tex
Update ethics statement [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/e1e2ef76a476174a4115937d77457037ddec95df.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/e1e2ef76a476174a4115937d77457037ddec95df/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/4786483649

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...d2e34990ccf22adba0dd011d640baf961cfecd6e}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/d2e34990ccf22adba0dd011d640baf961cfecd6e/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/d2e34990ccf22adba0dd011d640baf961cfecd6e}{habi/EAWAG-manuscript@d2e3499}
on April 24, 2023.

@@

The study used specimens from an already existing fish collectionm, built over decades of research led by Ole Seehausen and continuing until today.
All relevant permits for research, the permits for export from the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Available: \url{https://osf.io/ecmz4}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} of the manuscript to \href{https://www.reviewcommons.org/}{Review Commons}, aiming for \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...e1e2ef76a476174a4115937d77457037ddec95df}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/e1e2ef76a476174a4115937d77457037ddec95df}{habi/EAWAG-manuscript@e1e2ef7}
on April 24, 2023.

@@

The study used specimens from an already existing fish collection, built over decades of research led by Ole Seehausen and continuing until today.
All relevant permits for research, the permits for export from the respective country and import to Switzerland were given and the research has followed modern ethical guidelines for scientific research.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 24 Apr 2023{]}. Available: \url{https://osf.io/ecmz4/}}
